SPARQL on the Open, Decentralised Web

### 2016-11-15 dissertation/introduction.tex
Move the big problem statement

The present work is located at the confluence of several contemporary
efforts in the Semantic Web community. The focus is on query answering
with the SPARQL query language, with emphasis on exploiting the World
Wide Web, but it touches upon query federation, hypermedia, empiricial
methods for evaluating performance, standards compliance and even
philosophy of science. A comprehensive treatment of research problems
are given in Section~\ref{sec:problems}, but to understand the
following contributions, the overarching problems are as follows:

>>>>

The present work is located at the confluence of several contemporary
efforts in the Semantic Web community. The focus is on query answering
with the SPARQL query language, with emphasis on exploiting the World
Wide Web, but it touches upon query federation, hypermedia, empiricial
methods for evaluating performance, standards compliance and even
philosophy of science.

The overarching problem this work tries to address is this:

\begin{framed}
\begin{quote}
To achieve a Semantic Web where anyone can say anything about
anything, and where everyone is enabled to analyse data that have been
contributed, there is a difficult balance between centralising
infrastructure and decentralising it, and between processing on
clients and servers.
\end{quote}
\end{framed}

A comprehensive treatment of research problems is given in
Section~\ref{sec:problems}, but to understand the following
contributions, a superficial overview is provided:
